### 2024-06-24 basic-statistics.qmd
20240623 - coefficient of determination

Regression with one predictor takes the following form:

@@

Regression with multiple predictors—i.e., multiple regression—takes the following form:

@@

For instance, the *t* statistic from the independent-samples *t*-test and the *F* statistic from ANOVA can be thought of as the ratio of between-group variance to within-group variance:

@@

The correlation coefficient can be thought of as the ratio of shared variance (i.e., covariance) to total variance:

@@

>>>>

Regression with one predictor takes the form of @eq-regression:

@@

Regression with multiple predictors—i.e., multiple regression—takes the form of @eq-multipleRegression:

@@

For instance, the *t* statistic from the independent-samples *t*-test and the *F* statistic from ANOVA can be thought of as the ratio of between-group variance to within-group variance, as in @eq-tTestPartitionedVariance:

@@

The correlation coefficient can be thought of as the ratio of shared variance (i.e., covariance) to total variance, as in @eq-correlationPartitionedVariance:

@@

The coefficient of determination ($R^2$) is the proportion of variance in the [outcome variable](#sec-correlationalStudy) that is explained by the [predictor variables](#sec-correlationalStudy).
The coefficient of determination can be expressed as the ratio of variance explained in the [outcome variable](#sec-correlationalStudy) to the total variance in the [outcome variable](#sec-correlationalStudy), as in @eq-coefficientOfDetermination:

$$
R^2 = \frac{\text{variance explained in the outcome variable}}{\text{total variance in the outcome variable}}
$$ {#eq-coefficientOfDetermination}
